Model Estimation

### 2018-12-06 model_estimation.Rmd
//WIP on estimation

```{r read_parks, echo=FALSE}
parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
```

@@

```{r tweettransformation}
parks@data %>%
  tbl_df() %>%
  dplyr::select(raw = TWEET_COUNT) %>%
  filter(raw < 100) %>%
  mutate(
    `0.5` = yeo.johnson(raw, 0.5),
    `0` = yeo.johnson(raw, 0),
    log = log(raw)
  ) %>%
  gather(lambda, x, -raw) %>%
  ggplot(aes(x = raw, y = x, color = lambda)) + 
  geom_line()

parks@data <- parks@data %>%
  mutate(
    log_size = log(Park_Acres),
    log_tweets = yeo.johnson(TWEET_COUNT, 0)
  )

@@

parks@data <- tbl_df(parks@data)
```

@@

```{r W, echo=FALSE}
neighbors <- poly2nb(tracts, queen = TRUE)
W <- nb2listw(neighbours = neighbors, zero.policy = TRUE, style = "W")
print(W, zero.policy = TRUE)
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
ev <- eigenw(W)
```

@@

@@

  # calculate observed utility by adding the weighted park-level attributes 
  # to the columns of the matrix
  # V is n x p, with b added by-column to each element in a
  V <- sweep(a, MARGIN = 2, b, `+`)

@@

First, we calculate the distance between the tracts and the parks.
```{r distancematrix}
# calculate centroids of tracts and parks
tract_centroids <- gCentroid(tracts, byid = TRUE) 
park_centroids <- gCentroid(parks, byid = TRUE)

# distances from all tracts to all zones
distances <- log(gDistance(park_centroids, tract_centroids, byid = TRUE) / 5280)
```

@@

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 0), # distance, size 
  lower = c(-100, 0), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  hessian=TRUE, distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_lm, method = "L-BFGS-B", control = list(trace = 6))
```

>>>>

```{r read_parks, echo=FALSE}
parks <- sf::st_read("data/nyc_parks.geojson")
```

@@

```{r tweettransformation}
parks %>%
  tbl_df() %>%
  dplyr::select(raw = TWEET_COUNT) %>%
  filter(raw < 100) %>%
  mutate(
    `0.5` = yeo.johnson(raw, 0.5),
    `0` = yeo.johnson(raw, 0),
    log = log(raw)
  ) %>%
  gather(lambda, x, -raw) %>%
  ggplot(aes(x = raw, y = x, color = lambda)) + 
  geom_line()

parks <- parks %>%
  mutate(
    log_size = log(Park_Acres),
    log_tweets = yeo.johnson(TWEET_COUNT, 0)
  )

@@

@@

```{r W, echo=FALSE}
tracts.dnn <- dnearneigh(gCentroid(tracts, byid = TRUE), 0, 1.8 * 5280)
dists <- nbdists(tracts.dnn, gCentroid(tracts, byid = TRUE))
dists.inv <- lapply(dists, function(x) 1 / x)
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv, zero.policy = TRUE, style = "W")
print(W, zero.policy = TRUE)
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
```

@@

The residuals appear homoskedastic with few outliers.

```{r residuals}
tracts_sf <- tracts_sf[complete_tracts_index, ] %>%
  mutate(
    log_obesity = tracts$log_obesity,  
    obese_base_lm_residuals = obese_base_lm$residuals,
    obese_base_sdm_fitted = obese_base_sdm$fitted.values,  
    obese_base_sdm_residuals = obese_base_sdm$residual
  )

ggplot(tracts_sf, aes(x = log_obesity, y = obese_base_sdm_fitted)) + 
  geom_point()
```

The residuals also appear to be distributed wtihout serious spatial correlation
```{r residuals_map}
pal <- colorQuantile("BrBG", tracts_sf$obese_base_sdm_residuals, n = 9)
leaflet(tracts_sf) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(color = ~pal(obese_base_sdm_residuals), stroke = NA, opacity = 0.8)
```

@@

  # calculate observed utility by adding the weighted park-level attributes 
  # to the columns of the matrix
  # V is n x p, with b added by-column to each element in a
  V <- sweep(a, 2, b, `+`)

@@

First, we calculate the distance between the tracts and the parks.
```{r distancematrix}
# calculate centroids of tracts and parks
tract_centroids <- tracts %>% st_as_sf() %>% st_centroid() 
park_centroids <- parks %>% st_centroid() %>% st_transform(st_crs(tract_centroids))

# distances from all tracts to all zones
distances <- st_distance(park_centroids, tract_centroids, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()
```

@@

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 0), # distance, size 
  lower = c(-100, -100), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  hessian=TRUE, distances = log(distances[1:10, 1:10]), parks = parks[1:10,], tracts = tracts[1:10, ], 
  model = obese_base_lm, method = "L-BFGS-B", control = list(trace = 6))
```
